### 2015-12-13 mirror-descent.tex
minor removals of text
Fix typos, grammar, and bibliography.

\textsc{Mirror Descent} (MD) is a generic algorithm similar to \textsc{Follow The
Regularized Leader} but quite different in details. The algorithm is stated as
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer}. The algorithm is
parametrized by a sequence $\{R_t\}_{t=0}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}. Each regularizer $R_t$ can depend on past
loss vectors $\ell_1, \ell_2, \dots, \ell_t$ in an arbitrary way. If $R_t$ is
not differentiable\footnote{Note that this can happen even when $R_t$ is a
restriction of a differentiable function defined on a superset of $K$.  If $K$
is bounded and closed, $R_t$ fails to be differentiable at the boundary of $K$.
If $K$ is a subset of an affine subspace of a dimension smaller than the
dimension of $V$, then $R_t$ fails to be differentiable everywhere.}, the
Bregman divergence, $\Breg_{R_t}(u,v) = R_t(u) - R_t(v) - \langle \grad R_t(v),
u - v \rangle$ needs to be defined. This is done by choosing a subgradient map
$\grad R_t:K \to V$, i.e. a function such that $\grad R_t(w)$ is a subgradient
of $R_t$ at a point $w$. If $R_t$ is a restriction of a differentiable function
$R'_t$, it is convenient to define $\grad R_t(w) = \grad R'_t(w)$ for all $w
\in K$. The following lemma bounds regret of \textsc{MD}.  Proof
can be found
in~\cite{Rakhlin-Sridharan-2009,Duchi-Shalev-Shwartz-Singer-Tewari-2010}.  For
completeness we give a proof in~\ref{section:mirror-descent-proofs}.

@@

The most prominent instance of \textsc{MD} is \textsc{Projected Gradient
Descent} defined by the recurrence
$$
w_{t+1} = \Pi_K(w_t - \eta_t \ell_t)
$$
where $\Pi_K(x) = \argmin_{y \in K} \|x-y\|_2$ is the Euclidean projection to
$K$ and $\eta_t > 0$ is the step size.  \textsc{Projected Gradient Descent} is
an instance of \textsc{MD} with regularizer $R_t(w) =
\frac{1}{2\eta_t}\|w\|_2^2$.  A special case of projected gradient descent with
step size $\eta_t = \frac{1}{\sqrt{t}}$ is Zinkevich's \textsc{Generalized
Infinitesimal Gradient Ascent} (GIGA) algorithm~\cite{Zinkevich-2003}.
Full-matrix and diagonal versions of \textsc{AdaGrad with Composite MD
Update}~\cite{Duchi-Hazan-Singer-2011} are an instances of
\textsc{MD} for any bounded $K$ with regularizers
$$
R_t(w) = \frac{1}{2} w^\top \left(\sum_{i=1}^t \ell_i \ell_i^\top \right)^{1/2} \!\!\!\! w
\qquad \text{and} \qquad
R_t(w) = \frac{1}{2} \sum_{j=1}^d w_j^2 \sqrt{ \sum_{i=1}^t \ell_{i,j}^2}
$$
respectively. The diagonal version is simply the per-coordinate construction
applied to the one-dimensional version. When $d=1$, both algorithms are
equivalent to
\begin{equation}
\label{equation:ada-grad-regularizer}
R_t(w) = \frac{\|w\|_2^2}{2} \sqrt{\sum_{i=1}^t \|\ell_i\|_2^2 } \; .
\end{equation}
All three sequences of regularizers give a scale-free algorithm. Regularizer
\eqref{equation:ada-grad-regularizer} can be viewed as a scale-free
generalization of Zinkevich's GIGA algorithm. That is, when $\|\ell_i\|_2
= 1$ for all $i$, \textsc{MD} with regularizer
\eqref{equation:ada-grad-regularizer} coincides with GIGA.

Replacing $\frac{1}{2}\|w\|_2^2$ in equation
\eqref{equation:ada-grad-regularizer} with an arbitrary convex function $R:K
\to \R$ yields
\begin{equation}
\label{equation:scale-free-mirror-descent}
R_t(w) = R(w) \sqrt{\sum_{i=1}^t \|\ell_i\|_*^2} \; .
\end{equation}
We call the resulting algorithm \textsc{Scale-Free MD} with
regularizer $R$. Similar to \textsc{SOLO FTRL}, the regularizer
\eqref{equation:scale-free-mirror-descent} does not uniquely define
the \textsc{MD} minimizer
$w_{t+1} = \argmin_{w \in K} \left(\langle \ell_t, w \rangle + \Breg_{R_t}(w,
w_t) \right)$ when $\sqrt{\sum_{i=1}^t \|\ell_i\|_*^2}$ is zero.
This happens when the loss vectors $\ell_1, \ell_2, \dots, \ell_t$ are all
zero (and in particular for $t=0$). In this case, we define
$w_{t+1} = \argmin_{w \in K} R(w)$ which agrees with
$w_{t+1} = \lim_{a \to 0^+} \argmin_{w \in K} a \Breg_{R}(w, w_t)$.

The theorem below upper bounds the regret of \textsc{Scale-Free Mirror Descent}
(see also
\cite{Duchi-Hazan-Singer-2011,Duchi-Shalev-Shwartz-Singer-Tewari-2010,Rakhlin-Sridharan-2013}).
Proof is in~\ref{section:mirror-descent-proofs}.

\begin{theorem}[Regret of Scale-Free Mirror Descent]
\label{theorem:regret-scale-free-mirror-descent}
Suppose $K \subseteq V$ is a non-empty closed convex subset. Suppose that $R:K
\to \R$ is a $\lambda$-strongly convex function with respect to a norm
$\|\cdot\|$.  \textsc{Scale-Free Mirror Descent} with regularizer $R$ satisfies
for any $u \in K$,
$$
\Regret_T(u)
\le
\left( \frac{1}{\lambda} + \sup_{v \in K} \Breg_R(u,v) \right) \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{theorem}

@@

\begin{corollary}[Regret of Scale-Free Mirror Descent]
\label{corollary:regret-scale-free-mirror-descent}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset.  Suppose
that $f:K \to \R$ is a $1$-strongly convex function with respect to a norm
$\|\cdot\|$.  \textsc{Scale-Free Mirror Descent} with regularizer
$$
R(w) = \frac{f(w)}{\displaystyle \sqrt{\sup_{u,v \in K} \Breg_f(u,v)}}
\quad \text{satisfies} \quad %
\Regret_T \le 2 \sqrt{\sup_{u,v \in K} \Breg_f(u,v) \sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{corollary}

The regret bound for \textsc{Scale-Free Mirror Descent} in the
Corollary~\ref{corollary:regret-scale-free-mirror-descent} depends on
$\sup_{u,v \in K} \Breg_f(u,v)$. In contrast, the regret bounds for
\textsc{AdaFTRL} and \textsc{SOLO FTRL} in
Corollaries~\ref{corollary:ada-ftrl-regret-bound}~and~\ref{corollary:regret-solo-ftrl-bounded-set}
depend on $\sup_{u \in K} f(u)$.  Similarly, the regret bound in
Theorem~\ref{theorem:regret-scale-free-mirror-descent} for \textsc{Scale-Free
Mirror Descent} depends on $\sup_{v \in K} \Breg_R(u,v)$ and the regret bounds in
Theorems~\ref{theorem:ada-ftrl-regret-bound}~and~\ref{theorem:regret-solo-ftrl}
for \textsc{AdaFTRL} and \textsc{SOLO FTRL} depend on $R(u)$. It is not hard to
show that
\begin{equation}
\label{equation:regularizer-vs-divergence}
\forall u \in K \qquad R(u) \le \sup_{v \in K} \Breg_R(u,v)
\end{equation}
provided that at the minimizer $v^* = \argmin_{v \in K} R(v)$ both $R(v^*)$ and
$\grad R(v^*)$ are zero. Indeed, in that case, $R(u) = \Breg_R(u,v^*) \le
\sup_{v \in K} \Breg_R(u,v)$.

@@

Thus, \eqref{equation:regularizer-vs-divergence} implies that ignoring constant
factors, the regret bound for \textsc{Scale-Free Mirror Descent} is \emph{not}
better and possibly worse than the regret bounds for \textsc{AdaFTRL} and
\textsc{SOLO FTRL}.  In fact, it is not hard to come up with examples where
$R(u)$ is finite whereas $\sup_{v \in K} \Breg_R(u,v)$ is infinite. We mention
two such examples. The first example is $R(w) = \frac{1}{2}\|w\|_2^2$ defined
on the whole space $V$, where for any $u \in V$, $R(u)$ is a finite value but
$\sup_{v \in K} \Breg_R(u,v) = \sup_{v \in V} \frac{1}{2}\|u-v\|_2^2 =
+\infty$. The second example is the negative entropy regularizer $R(w) = \ln d
+ \sum_{j=1}^d w_j \ln w_j$ defined on the $d$-dimensional probability simplex
$K = \{ w \in \R^d ~:~ w_j \ge 0, \sum_{j=1}^d w_j = 1 \}$, where for any $u
\in K$, $R(u)$ is finite and in fact lies in the interval $[-\ln d, 0]$ but
$\sup_{v \in K} \Breg_R(u,v) = \sup_{v \in K} \sum_{j=1}^d u_j \ln(u_j/v_j) = +
\infty$. We return to these examples in the following subsection.

\subsection{Lower Bounds}
\label{subsection:mirror-descent-lower-bound}

The bounds in Theorem~\ref{theorem:regret-scale-free-mirror-descent} and
Corollary~\ref{corollary:regret-scale-free-mirror-descent} are vacuous when
$\Breg_R(u,v)$ is not bounded. One might wonder if the assumption that
$\Breg_R(u,v)$ is bounded is necessary in order for \textsc{Scale-Free Mirror
Descent} to have a ``small'' regret. We show necessity of this assumption on
two counter-examples.  In these counter-examples, we consider strongly convex
regularizers $R$ such that $\Breg_R(u,v)$ is not bounded and we construct
sequences of loss vectors $\ell_1, \ell_2, \dots, \ell_T$ such that
$\|\ell_1\|_* = \|\ell_2\|_* = \dots = \|\ell_T\|_* = 1$ and \textsc{Scale-Free
Mirror Descent} has regret $\Omega(T)$ or worse.

The first counter-example is stated as
Theorem~\ref{theorem:first-counter-example} below. The decision set is the
whole space $K=V$ and the regularizer is $R(w) = \frac{1}{2}\|w\|_2^2$. Note
that $R(w)$ is $1$-strongly convex with respect to $\|\cdot\|_2$ and the dual
norm of $\|\cdot\|_2$ is $\|\cdot\|_2$. The corresponding Bregman divergence is
$\Breg_R(u,v) = \frac{1}{2}\|u-v\|_2^2$. The counter-example constructs
sequence of unit-norm loss vectors in the one-dimensional subspace spanned by
the first vector of the standard unit basis.  On such sequence, Zinkevich's
\textsc{GIGA} and both versions of \textsc{AdaGrad with Composite Mirror
Update} have predictions identical to \textsc{Scale-Free Mirror Descent}. Hence
the lower bound applies to all four algorithms.

\begin{theorem}[First Counter-Example]
\label{theorem:first-counter-example}
Suppose $K = V$. For any $T \ge 42$, there exists a sequence of loss vectors
$\ell_1, \ell_2, \dots, \ell_T \in V^*$ such that $\|\ell_1\|_2 = \|\ell_2\|_2
= \dots = \|\ell_T\|_2 = 1$ and \textsc{Scale-Free Mirror Descent} with
regularizer $R(w) = \frac{1}{2}\|w\|_2^2$, Zinkevich's \textsc{GIGA} algorithm,
and both versions of \textsc{AdaGrad with Composite Mirror Descent Update}
satisfy
$$
\Regret_T(0) \ge \frac{T^{3/2}}{20} \; .
$$
\end{theorem}

>>>>

\textsc{Mirror Descent} (MD) is a generic algorithm similar to \textsc{FTRL}
but quite different in details. The algorithm is stated as
Algorithm~\ref{algorithm:mirror-descent-varying-regularizer}. The algorithm is
parametrized by a sequence $\{R_t\}_{t=0}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}. Each regularizer $R_t$ can depend on past
loss vectors $\ell_1, \ell_2, \dots, \ell_t$ in an arbitrary way. If $R_t$ is
not differentiable\footnote{Note that this can happen even when $R_t$ is a
restriction of a differentiable function defined on a superset of $K$.  If $K$
is bounded and closed, $R_t$ fails to be differentiable at the boundary of $K$.
If $K$ is a subset of an affine subspace of a dimension smaller than the
dimension of $V$, then $R_t$ fails to be differentiable everywhere.}, the
Bregman divergence, $\Breg_{R_t}(u,v) = R_t(u) - R_t(v) - \langle \grad R_t(v),
u - v \rangle$ needs to be defined. This is done by choosing a subgradient map
$\grad R_t:K \to V$, i.e. a function such that $\grad R_t(w)$ is a subgradient
of $R_t$ at a point $w$. If $R_t$ is a restriction of a differentiable function
$R'_t$, it is convenient to define $\grad R_t(w) = \grad R'_t(w)$ for all $w
\in K$. The following lemma bounds regret of \textsc{MD}.  Proof can be found
in~\cite{Rakhlin-Sridharan-2009,Duchi-Shalev-Shwartz-Singer-Tewari-2010}.  For
completeness we give a proof in~\ref{section:mirror-descent-proofs}.

@@

The most prominent instance of \textsc{MD} is \textsc{Projected Gradient
Descent} defined by the recurrence
$$
w_{t+1} = \Pi_K(w_t - \eta_t \ell_t)
$$
where $\Pi_K(x) = \argmin_{y \in K} \|x-y\|_2$ is the Euclidean projection to
$K$ and $\eta_t > 0$ is the step size.  \textsc{Projected Gradient Descent} is
an instance of \textsc{MD} with regularizer $R_t(w) =
\frac{1}{2\eta_t}\|w\|_2^2$.  A special case of \textsc{Projected Gradient
Descent} with step size $\eta_t = \frac{1}{\sqrt{t}}$ is \textsc{Generalized
Infinitesimal Gradient Ascent} (GIGA)~\cite{Zinkevich-2003}.  Full-matrix and
diagonal versions of \textsc{AdaGrad with Composite MD
Update}~\cite{Duchi-Hazan-Singer-2011} are an instances of \textsc{MD} for any
bounded $K$ with regularizers
$$
R_t(w) = \frac{1}{2} w^\top \left(\sum_{i=1}^t \ell_i \ell_i^\top \right)^{1/2} \!\!\!\! w
\qquad \text{and} \qquad
R_t(w) = \frac{1}{2} \sum_{j=1}^d w_j^2 \sqrt{ \sum_{i=1}^t \ell_{i,j}^2}
$$
respectively. The diagonal version is simply the per-coordinate construction
applied to the one-dimensional version. When $d=1$, both algorithms are
equivalent to
\begin{equation}
\label{equation:ada-grad-regularizer}
R_t(w) = \frac{\|w\|_2^2}{2} \sqrt{\sum_{i=1}^t \|\ell_i\|_2^2 } \; .
\end{equation}
All three sequences of regularizers give a scale-free algorithm. Regularizer
\eqref{equation:ada-grad-regularizer} can be viewed as a scale-free
generalization of GIGA. That is, when $\|\ell_i\|_2
= 1$ for all $i$, \textsc{MD} with regularizer
\eqref{equation:ada-grad-regularizer} coincides with GIGA.

Replacing $\frac{1}{2}\|w\|_2^2$ in equation
\eqref{equation:ada-grad-regularizer} with an arbitrary convex function $R:K
\to \R$ yields
\begin{equation}
\label{equation:scale-free-mirror-descent}
R_t(w) = R(w) \sqrt{\sum_{i=1}^t \|\ell_i\|_*^2} \; .
\end{equation}
We call the resulting algorithm \textsc{Scale-Free MD} with
regularizer $R$. Similar to \textsc{SOLO FTRL}, the regularizer
\eqref{equation:scale-free-mirror-descent} does not uniquely define
the \textsc{MD} minimizer
$w_{t+1} = \argmin_{w \in K} \left(\langle \ell_t, w \rangle + \Breg_{R_t}(w,
w_t) \right)$ when $\sqrt{\sum_{i=1}^t \|\ell_i\|_*^2}$ is zero.
This happens when the loss vectors $\ell_1, \ell_2, \dots, \ell_t$ are all
zero. In this case, we define
$w_{t+1} = \argmin_{w \in K} R(w)$ which agrees with
$w_{t+1} = \lim_{a \to 0^+} \argmin_{w \in K} a \Breg_{R}(w, w_t)$.
Similarly, $w_1 = \argmin_{w \in K} R(w)$.

The theorem below upper bounds the regret of \textsc{Scale-Free MD} (see also
\cite{Duchi-Hazan-Singer-2011,Duchi-Shalev-Shwartz-Singer-Tewari-2010,Rakhlin-Sridharan-2013}).
Proof is in~\ref{section:mirror-descent-proofs}.

\begin{theorem}[Regret of Scale-Free Mirror Descent]
\label{theorem:regret-scale-free-mirror-descent}
Suppose $K \subseteq V$ is a non-empty closed convex subset. Suppose that $R:K
\to \R$ is a $\lambda$-strongly convex function with respect to a norm
$\|\cdot\|$.  \textsc{Scale-Free MD} with regularizer $R$ satisfies
for any $u \in K$,
$$
\Regret_T(u)
\le
\left( \frac{1}{\lambda} + \sup_{v \in K} \Breg_R(u,v) \right) \sqrt{\sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{theorem}

@@

\begin{corollary}[Regret of Scale-Free Mirror Descent]
\label{corollary:regret-scale-free-mirror-descent}
Suppose $K \subseteq V$ is a non-empty bounded closed convex subset.  Suppose
that $f:K \to \R$ is a $1$-strongly convex function with respect to a norm
$\|\cdot\|$.  \textsc{Scale-Free MD} with regularizer
$$
R(w) = \frac{f(w)}{\displaystyle \sqrt{\sup_{u,v \in K} \Breg_f(u,v)}}
\quad \text{satisfies} \quad %
\Regret_T \le 2 \sqrt{\sup_{u,v \in K} \Breg_f(u,v) \sum_{t=1}^T \|\ell_t\|_*^2} \; .
$$
\end{corollary}

The regret bound for \textsc{Scale-Free Mirror Descent} in the
Corollary~\ref{corollary:regret-scale-free-mirror-descent} depends on
$\sup_{u,v \in K} \Breg_f(u,v)$. In contrast, the regret bounds for
\textsc{AdaFTRL} and \textsc{SOLO FTRL} in
Corollaries~\ref{corollary:ada-ftrl-regret-bound}~and~\ref{corollary:regret-solo-ftrl-bounded-set}
depend on $\sup_{u \in K} f(u)$.  Similarly, the regret bound in
Theorem~\ref{theorem:regret-scale-free-mirror-descent} for \textsc{Scale-Free
MD} depends on $\sup_{v \in K} \Breg_R(u,v)$ and the regret bounds in
Theorems~\ref{theorem:ada-ftrl-regret-bound}~and~\ref{theorem:regret-solo-ftrl}
for \textsc{AdaFTRL} and \textsc{SOLO FTRL} depend on $R(u)$. It is not hard to
show that
\begin{equation}
\label{equation:regularizer-vs-divergence}
\forall u \in K \qquad R(u) \le \sup_{v \in K} \Breg_R(u,v)
\end{equation}
provided that at the minimizer $v^* = \argmin_{v \in K} R(v)$ both $R(v^*)$ and
$\grad R(v^*)$ are zero. Indeed, in that case, $R(u) = \Breg_R(u,v^*) \le
\sup_{v \in K} \Breg_R(u,v)$.

@@

Thus, \eqref{equation:regularizer-vs-divergence} implies that ignoring constant
factors, the regret bound for \textsc{Scale-Free MD} is inferior to the regret
bounds for \textsc{AdaFTRL} and \textsc{SOLO FTRL}.  In fact, it is not hard to
come up with examples where $R(u)$ is finite whereas $\sup_{v \in K}
\Breg_R(u,v)$ is infinite. We mention two such examples. The first example is
$R(w) = \frac{1}{2}\|w\|_2^2$ defined on the whole space $V$, where for any $u
\in V$, $R(u)$ is a finite value but $\sup_{v \in K} \Breg_R(u,v) = \sup_{v \in
V} \frac{1}{2}\|u-v\|_2^2 = +\infty$. The second example is the negative
entropy regularizer $R(w) = \ln d + \sum_{j=1}^d w_j \ln w_j$ defined on the
$d$-dimensional probability simplex $K = \{ w \in \R^d ~:~ w_j \ge 0,
\sum_{j=1}^d w_j = 1 \}$, where for any $u \in K$, $R(u)$ is finite and in fact
lies in the interval $[-\ln d, 0]$ but $\sup_{v \in K} \Breg_R(u,v) = \sup_{v
\in K} \sum_{j=1}^d u_j \ln(u_j/v_j) = + \infty$. We return to these examples
in the following subsection.

\subsection{Lower Bounds for Mirror Descent}
\label{subsection:mirror-descent-lower-bound}

The bounds in Theorem~\ref{theorem:regret-scale-free-mirror-descent} and
Corollary~\ref{corollary:regret-scale-free-mirror-descent} are vacuous when
$\Breg_R(u,v)$ is not bounded. One might wonder if the assumption that
$\Breg_R(u,v)$ is bounded is necessary in order for \textsc{Scale-Free MD} to
have a ``small'' regret. We show necessity of this assumption on two
counter-examples.  In these counter-examples, we consider strongly convex
regularizers $R$ such that $\Breg_R(u,v)$ is not bounded and we construct
sequences of loss vectors $\ell_1, \ell_2, \dots, \ell_T$ such that
$\|\ell_1\|_* = \|\ell_2\|_* = \dots = \|\ell_T\|_* = 1$ and \textsc{Scale-Free
MD} has regret $\Omega(T)$ or worse.

The first counter-example is stated as
Theorem~\ref{theorem:first-counter-example} below. The decision set is the
whole space $K=V$ and the regularizer is $R(w) = \frac{1}{2}\|w\|_2^2$. Note
that $R(w)$ is $1$-strongly convex with respect to $\|\cdot\|_2$ and the dual
norm of $\|\cdot\|_2$ is $\|\cdot\|_2$. The corresponding Bregman divergence is
$\Breg_R(u,v) = \frac{1}{2}\|u-v\|_2^2$. The counter-example constructs
sequence of unit-norm loss vectors in the one-dimensional subspace spanned by
the first vector of the standard unit basis.  On such sequence, Zinkevich's
\textsc{GIGA} and both versions of \textsc{AdaGrad MD} have predictions
identical to \textsc{Scale-Free MD}. Hence the lower bound applies to all four
algorithms.

\begin{theorem}[First Counter-Example]
\label{theorem:first-counter-example}
Suppose $K = V$. For any $T \ge 42$, there exists a sequence of loss vectors
$\ell_1, \ell_2, \dots, \ell_T \in V^*$ such that $\|\ell_1\|_2 = \|\ell_2\|_2
= \dots = \|\ell_T\|_2 = 1$ and \textsc{Scale-Free MD} with
regularizer $R(w) = \frac{1}{2}\|w\|_2^2$, \textsc{GIGA},
and both versions of \textsc{AdaGrad MD} satisfy
$$
\Regret_T(0) \ge \frac{T^{3/2}}{20} \; .
$$
\end{theorem}

### 2015-12-13 preliminaries.tex
Fix typos, grammar, and bibliography.

Our scale-free online learning algorithms are instances of \textsc{FTRL} with
\emph{varying regularizers}, presented as
Algorithm~\ref{algorithm:ftrl-varying-regularizer}.  The algorithm is
paramatrized by a sequence $\{R_t\}_{t=1}^\infty$ of convex functions $R_t:K
\to \R$ called \emph{regularizers}.  Each regularizer $R_t$ can depend on the
past loss vectors $\ell_1, \ell_2, \dots, \ell_{t-1}$ in an arbitrary way.  The
following lemma bounds its regret.

\begin{lemma}[Regret of Follow The Regularized Leader]
\label{lemma:generic-regret-bound}
For any sequence $\{R_t\}_{t=1}^\infty$ of strongly convex lower
semi-continuous regularizers, the regret of
Algorithm~\ref{algorithm:ftrl-varying-regularizer} is upper
bounded as
$$
\Regret_T(u) \le R_{T+1}(u) + R_1^*(0) + \sum_{t=1}^{T} \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \; .
$$
\end{lemma}

>>>>

Two of our scale-free algorithms are instances of \textsc{FTRL} with
\emph{varying regularizers}, presented as
Algorithm~\ref{algorithm:ftrl-varying-regularizer}.  The algorithm is
paramatrized by a sequence $\{R_t\}_{t=1}^\infty$ of functions $R_t:K \to \R$
called \emph{regularizers}.  Each regularizer $R_t$ can depend on the past loss
vectors $\ell_1, \ell_2, \dots, \ell_{t-1}$ in an arbitrary way.  The following
lemma bounds its regret.

\begin{lemma}[Regret of Follow The Regularized Leader]
\label{lemma:generic-regret-bound}
If the regularizers $R_1, R_2, \dots$ chosen by
Algorithm~\ref{algorithm:ftrl-varying-regularizer} are strongly convex and lower
semi-continuous, the algorithm's regret is upper bounded as
$$
\Regret_T(u) \le R_{T+1}(u) + R_1^*(0) + \sum_{t=1}^{T} \Breg_{R_t^*}(-L_t, -L_{t-1}) - R_t^*(-L_t) + R_{t+1}^*(-L_t) \; .
$$
\end{lemma}
